Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd

## Swing State Polling Prediction Model
However, @fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the days until the election. This support rate changes model exhibits a higher rate of growth in Donald Trump's share of support. Although Kamala Harris is in the lead, Donald Trump's growth of support rate is an element that could stifle Harris' lead and drop her below her required 270 electoral votes. 
```{r}
#| label: fig-4
#| fig-cap: "Swing State Polling Prediction Model"
#| echo: false
#| warning: false
#| message: false

>>>>

## Swing State Polling Prediction Model

@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.We predicts that Kamala Harris may win based on our model.
However, this shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the days until the election. This support rate changes model exhibits a higher rate of growth in Donald Trump's share of support. Although Kamala Harris is in the lead, Donald Trump's growth of support rate is an element that could stifle Harris' lead and drop her below her required 270 electoral votes.

```{r}
#| label: fig-4
#| fig-cap: "Swing State Polling Prediction Model"
#| echo: false
#| warning: false
#| message: false
